---
title: "rjmb: Readme and Manual"
output:
  github_document:
    toc: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![Travis build status](https://travis-ci.org/jannikbuhr/rjmb.svg?branch=master)](https://travis-ci.org/jannikbuhr/rjmb)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of rjmb is to provide some helper functions for
data analysis and visualization in R.

All the little things I run into end up here.

# Installation

<!-- You can install the released version of rjmb from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rjmb") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jannikbuhr/rjmb")
```
# Usage

```{r}
library(rjmb)
library(tidyverse)

theme_set(theme_classic())
```

## Big Changes

### String Addition

Note, that loading this package overrides to `+`-operator to work
with strings (i.e. character vectors) as well^[this is similar to python].
For non-strings, the default primitive `+` is still used so this
should not break any existing code unless it relies on addition of
strings failing. Internally, it uses `paste`, thus numbers
are silently converted to strings when added to strings. As the first
type (LHS of `+`) determines method dispatch, when adding strings
and numbers, the first argument needs to be a string
(can be an empty string `""`).

```{r string-example}
"Hello " + "World"
"" + 1 + " duck."
x = 2
"" + x + " ducks."
```
## Helper Functions

### str_to_math()

Adding expressions from strings containing whitespace to a plot.

```{r example, fig.width=7, fig.height=1}
df <- tibble(
  x = c("delta+1", "Delta AB", "alpha"),
  y = rep(1, length(x))
)

df %>%
  ggplot(aes(x, y)) +
  geom_point() +
  scale_x_discrete(labels = str_to_math()) +
  theme(axis.text.x = element_text(size = 12))
```
